---
title: "ESm 262 Assignment 1"
author: "Jasmine"
date: "5/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Read In Data
```{r, warning=FALSE,message=FALSE}
library(tidyverse)
library(here)
```

```{r}
#Read in the zip file data
sb_raw <-
  read_delim(
    "parcels.csv.zip",
    delim = ",",
    col_types = cols(.default = col_character()))
```


```{r}
#Manually change the class types to match the parsel_columns.pdf designations

sb11 <-
  transmute(sb_raw,
    ID         = parse_character(APN, na = "NA"),
    SA1        = parse_character(Situs1, na = "NA"),
    SA2        = parse_character(Situs2, na = "NA"),
    Acre       = parse_number(Acreage,na = "NA"),
    UseCode    = parse_character(UseCode),
    NonTaxCode = parse_character(NonTaxCode, na = "NA"),
    AgPres     = parse_character(AgPres),
    Value      = parse_integer(LandValue),
    Net_Impr   = parse_integer(Net_Impr),
    Net_AV     = parse_integer(Net_AV),
    Address1   = parse_character(M_Address1, na = "NA"),
    Address2   = parse_character(M_Address2, na = "NA")
  )

sb11
```

```{r}

#Change data to csv
sbcsv <- write_delim(sb11,
  "sb2011.csv",
  delim = "|",
  na = ""
)

```
###Analyize 

####**Create R code snippets that answer the following questions about Santa Barbara county:**

#####*What are the 10 most-frequently-occuring land uses (in descending order)?*
*Hint: Load the UseCodes into a separate tibble, then join it to the parcels tibble.*
```{r}

#Pull UseCodes from Sb data
use<- data.frame(table(sb11$UseCode))
  colnames(use) <- c("UseCode","freq")

#Create UseCode Tibble
usetype <-
  read_delim(
    "UseCodes.csv",
    delim = "|",
    col_types = cols(.default = col_character()))

#Merge Data and get top 10
topuse<- merge.data.frame(use, usetype, by= "UseCode")  %>% 
        select("UseCode","freq","CodeDesc") %>% 
        arrange(desc(freq)) %>% 
       head(n=10)

 
DT::datatable(topuse)
```

#####*How many acres are in agricultural preserves?*
*Assume agricultural preserves are indicated by non-NA values for AgPres.*
```{r}
#Pull out only agricultural preserve acres
ag<- sb11 %>% 
  left_join(usetype, by = "UseCode") %>% 
  select(UseCode, CodeDesc, Acre) %>% 
  filter(!is.na(UseCode), UseCode == 5443) %>% 
  filter(!is.na(Acre))

#Get Sum
sum(ag$Acre)
  
```

#####*What is the mean net assessed value per acre of the entire county?*
*i.e., as if the entire county were a single parcel.*
```{r}

#Get mean of total Net_AV By Acre
AV<- mean(sb11$Net_AV)
Acre<- mean(sb11$Acre)

meanAV <- AV/Acre
meanAV

```


#####*What is the total net assessed value of all non-taxable parcels?*
*Assume non-taxable parcels are indicated by non-NA values for NonTaxCode.*
```{r}

#Pull out non taxed parcels only
notax<- sb11 %>% 
  select(Net_AV, NonTaxCode) %>% 
  filter(!is.na(NonTaxCode))

#Get Sum
sum(notax$Net_AV)

```

#####*What are the 10 largest property holders, by acreage?*
*Use the complete mailing address for tax statements as a proxy for the parcel owner. Ignore parcels where either component of the address is NA.*
```{r}
#Pull out acres with full property information
propowners<- sb11 %>% 
  select(Acre, Address1, Address2) %>% 
  filter(!is.na(Address1)) %>% 
   filter(!is.na(Address2)) %>% 
  arrange(desc(Acre)) %>% 
  head(n=10)
  
DT::datatable(propowners)

```

#####*What are the 10 largest property holders, by net assessed value?*
```{r}
#Pull our Net_AV with full property information
propnet<- sb11 %>% 
  select(Net_AV, Address1, Address2) %>% 
  filter(!is.na(Address1)) %>% 
   filter(!is.na(Address2)) %>% 
   arrange(desc(Net_AV)) %>% 
   head(n=10)
  
DT::datatable(propnet)

```


