---
title: "ESM 262 Assignment 2 Vazin"
author: "Jasmine"
date: "5/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


###Read In Data
```{r, warning=FALSE,message=FALSE}
library(tidyverse)
library(here)
here()
```

```{r}
#Read in the zip file data
sb_raw <-
  read_delim(
    "parcels.csv.zip",
    delim = ",",
    col_types = cols(.default = col_character()))

usetype <-
  read_delim(
    "UseCodes.csv",
    delim = "|",
    col_types = cols(.default = col_character()))
```


```{r}
#Manually change the class types to match the parsel_columns.pdf designations

sb11 <-
  transmute(sb_raw,
    ID         = parse_character(APN, na = "NA"),
    SA1        = parse_character(Situs1, na = "NA"),
    SA2        = parse_character(Situs2, na = "NA"),
    Acre       = parse_number(Acreage,na = "NA"),
    UseCode    = parse_character(UseCode),
    NonTaxCode = parse_character(NonTaxCode, na = "NA"),
    AgPres     = parse_character(AgPres),
    Value      = parse_integer(LandValue),
    Net_Impr   = parse_integer(Net_Impr),
    Net_AV     = parse_integer(Net_AV),
    Address1   = parse_character(M_Address1, na = "NA"),
    Address2   = parse_character(M_Address2, na = "NA")
  )

sb11
```

```{r}

#Create Database
parcels <- write_delim(sb11,
  "parcels.csv",
  delim = "|",
  na = ""
)

library(DBI)
db <- dbConnect(RSQLite::SQLite(), dbname = "parcel.db")

dbWriteTable(conn = db, name="UseCodes", value= usetype, overwrite=TRUE)

dbWriteTable(conn = db, name="parcels", value= parcels, overwrite=TRUE)

```
###Analyize 

#####*1. What are the 10 most-frequently-occuring land uses (in descending order)?*
*Hint: Load the UseCodes into a separate tibble, then join it to the parcels tibble.*
```{sql connection=db}


SELECT CodeDesc, COUNT(CodeDesc) AS topuse
FROM parcels JOIN usecodes
ON parcels.UseCode = usecodes.Usecode
GROUP BY parcels.Usecode
ORDER BY topuse DESC
LIMIT 10



```

#####*2. How many acres are in agricultural preserves?*
*Assume agricultural preserves are indicated by non-NA values for AgPres.*
```{sql connection=db}

SELECT SUM(Acre) FROM parcels WHERE AgPres IS NOT NULL 
  
```

#####*3. What is the mean net assessed value per acre of the entire county?*
*i.e., as if the entire county were a single parcel.*
```{sql connection=db}

SELECT AVG(Net_AV)/AVG(Acre)
FROM parcels
WHERE Acre IS NOT NULL 
AND Net_AV IS NOT NULL
AND Acre >=0


```


#####*4. What is the total net assessed value of all non-taxable parcels?*
*Assume non-taxable parcels are indicated by non-NA values for NonTaxCode.*
```{sql connection=db}

SELECT SUM(Net_AV) FROM parcels WHERE NonTaxCode IS NOT NULL

```

#####*5. What are the 10 largest property holders, by acreage?*
*Use the complete mailing address for tax statements as a proxy for the parcel owner. Ignore parcels where either component of the address is NA.*
```{sql connection=db}

SELECT Address1, Address2, SUM(Acre) AS acres
FROM parcels
WHERE Address1 AND Address2 IS NOT NULL
GROUP BY Address1, Address2
ORDER BY acres DESC
LIMIT 10

```

#####*6. What are the 10 largest property holders, by net assessed value?*
```{sql connection=db}

SELECT Address1, Address2, SUM(Net_AV) AS value
FROM parcels
WHERE Address1 AND Address2 IS NOT NULL
AND Net_AV IS NOT NULL
GROUP BY Address1, Address2
ORDER BY value DESC
LIMIT 10

```